---
title: "Research Log & Notes"
author: "Jérémy Genette"
date: "Latest Sync: `r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    theme: journal
    highlight: pygments
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Trigger Git actions automatically AFTER the document is completely finished rendering
knitr::knit_hooks$set(document = function(x) {
  message("--- Auto-Pushing to GitHub ---")
  try({
    # Track both the source file and the compiled website file
    gert::git_add(c("Notes_2026.Rmd", "Notes_2026.html"))
    gert::git_commit(paste("Auto-update:", Sys.Date()))
    gert::git_push(remote = "origin", refspec = "refs/heads/main")
    message("--- Push Complete! ---")
  })
  return(x) 
})

```

# To-Do

## \### High Priority

### Medium Priority

-   Speak JC about this technique

## \### Low Priority

------------------------------------------------------------------------

# Research ideas

-   According to Hanne, Flemish still perceive phonoloogical voicing difference between g and ch, but the voicing is not to be seen in the phonetic voicing of the fricative 🇧🇪

# Devoicing in Belgian French 🇧🇪

Oui, ta présentation s'est très bien passée et les commentaires d'Adèle sont juste à propos de l'environnement.

-   position in the utterance final
-   encoding of phonological length in Belgium

## Control of phonetic context

## combien de monosyllabe/bisyllabic/multi

### Phrase lexicale: position relative

Prosogram - profil - noyau syllabique - Polytonia moins de devoisement en position forte (avec plus de voisement)

-   when selecting CVC syllables and only the one in coda... if we select non-word-final syllable... there is always a consonant after that

Je pense que les résultats montrent qu'il y a un léger dévoisement en France, mais il est variable.

A mon avis, on devrait creuser un peu plus, en utilisant ma méthode de détection de voisement + f0 et les intégrer dans le modèle.

Concernant la régression logistique, il faudrait qu'on calcule le VIF pour voir s'il y a une multicolinéarité élevée ou pas. Tu peux regarder ici :

<https://jalalal-tamimi.github.io/R-Stats-Linguistics-Book/8.5-issues-with-glm-and-regression-analyses-in-general.html#checking-collinearity>

### Boosting machines

Mais on devrait regarder un peu plus avec les forêts aléatoires et peut-être gradient boosting machines (que j'ai utilisé pour RFP).

## cross correlation

ac: intonation cc: voiced quality

## RF avec données catégorielles

-   il faut utiliser des "one hot encoding"

## Multilevelmod package

pour utiliser plusieurs cores en même temps

## Modèles à faire

1 france + voix vs be + voix vs fr + non voix

Lieu d'articulation à ajouter

Lieu de phrases (utteranc-initial vs utterance-final vs utterance-medial)

# Matériel à acheter

## EGG parole

vocevista mais c'est fait seulement pour le chant 850+300

egg recherche 3000 euro (glottal enterprises)

## enregisteur ZOOM H6 + stereo + headmounted

carte audio + focusrite

casque pour connecter au zoom

Splitter pour enregistrer en stereo

si perception en lab - casque de hautes qualités

## Magasin

Thomanns

pour MAC M5

stockage

# Nasality (NAF-Chris Carrignan)

NAF + MFCC

rhinopharangality en lien avec le LAM

Interesting for JC

crosslinguistic effect

-   Do the NAF features also capture voiceless nasals ? Typical features should not work but others well... and it's just the idea that you work from bottom up approach... (compare <https://www.journal-labphon.org/article/id/9152/#B47>: instead of nasal vs oral - do nasal vs aspirates)

We should compare

-   Will Styler PHD (<https://wstyler.ucsd.edu/files/styler_dissertation_final.pdf>)
    -   Good decription of the features (<https://wstyler.ucsd.edu/files/styler2017_jasa_onacousticalnatureofnasality.pdf>)

# RFP - 1-3/07/2026

-   **Keynote talk: Of sonority, features and markedness** - Joaquim Brandao de Carvalho

  - Quand la manière d'articulation se propage par -> le lieu se propgae aussi
  Notion de modes est à la base des principes de SSP (sonorité) not always!!!!
  
  cluster heterosyllabic n'ont pas de c-center (brownman, goldstein)
  
  Old french /l/ est conservé en attqaue eou en position finale mais pas devant consonne
  
  Jakobson: la marque doit être empirique (typologie ou bien acquisitationelle- Ikwut_ukwa 2025 for probabilistic account)
  
  - Sonorité
  - Marque 
  - Trait de phonation

-   *A unified licensing approach to Valencian vowel harmony* - Ricard Herrero, Jesús Jiménez, Maria-Rosa Lloret

-   *Polish Nasal Assimilation is governed by faithfulness to place nodes* - Tomek Łuszczek

-   *A Formal Analysis of so-called “weak” and “limited” High Tones in Magdalena Peñasco Mixtec* - Thom Van Hugte

-   *Réanalyse phonétique et phonologique du système tonal du musey* - Lora Litvinova, Albert Camus Soulokadi

  - Toneme (=phonological tone) vs (phonetic) tone


-   *L'émergence de l'accent initial en français langue maternelle* - Guillaume ROUX, Germana Carolina Soler Millán

  - accent primaire Jun 1 Fougeron vs secondaire (Di Cristo 2000)
  - développement longitudinal de l'accent initiale en français

-   *Quand on interroge la phonologie, c'est l'orthographe qui répond ! L'utilisation des correspondances entre syllabes orales et écrites dans une tâche phonologique* - Samantha Ruvoletto

-   **Keynote talk** - Ghada Khattab

-   *Temporal Stability in Consonant+Vowel Sequences In Tashlhiyt: An Acoustic Study* - Abdelaziz Bazzi

-   *British Accents and Phonological Awareness in the Language Classroom: An Exploratory Study in Upper Secondary Education* - Alison May LAGARDE

-   *The [n̩]s and outs of syllabic theory, as illustrated by the syllabic /n/ of Yiddish In* - Noam Faust, Tobias Scheer

-   *Vowel harmony and feature shift in Eastern Black Sea Turkish* - Stefano Canalis, Mehmet Can Dadan

-   *Splitting Government and Licensing: Debuccalization, Vowel Epenthesis and Pseudogeminates in Forest Nenets* - Kirill Medushevsky

-   *Articulatory and acoustic correlates of laryngeal changes associated with [Constricted Epilaryngeal Tube] in Arabic guttural consonants* - Jalal Al-Tamimi

-   *Predicting the Unpredictable: The Case of Moroccan Arabic Broken Plurals* - Ali Nirheche

-   *Strict domination in probabilistic phonology* - Giorgio Magri, Edward Flemming

-   **Keynote talk** - Pierre-Yves Testenoire

-   *Phonemic overlapping in structuralist phonology* - Stefano Canalis

-   *L'invention de la phonologie : Prague ou Genève ?* - Gabriel Bergounioux

-   *Pour une épistémologie rétrospective en phonologie : Georges Millardet et l'anticipation des modèles autosegmentaux et gabaritiques* - Jean Léonard LEONARD

-   *Réconciliation aux frontières : l'approche générative de la phonologie diachronique du chinois dans les années 1970-1980* - Xiaoliang Luo

-   **Keynote talk** - Mary Walworth

-   *Phonologie et persuasion : analyse prosodique des discours présidentiels sur la prévention de la COVID-19* - Husam MA'AYAH

-   *Mapping Breton Stress: Acoustic Correlates and Social Profiles in Perception* - Seongwoo KANG

-   *Tonal constraints on metrical variation in Chinese regulated verse* - Yuxuan Lang

-   *Examining the impact of ASR on Spanish pronunciation acquisition* - Christina Garcia, Dan Nickolai

-   *Free-Variation in the Bangla Coronal Sub-Space: A Stochastic OT Approach* - Sayantan Mandal, Rakesh Sengupta

-   *Are Phonological Contrasts a Question of the Quantity of Phonetic Information? The Case of Intrinsic Vowel Pitch in Back and Front Vowels* - Jérémy Genette

-   *Velarization of the alveolo-palatal consonants in Nanjiang Gan (Sinitic) in China* - Daxingwang Peng

-   *Allomorphie du pronom possessif 3SG.M en Darija : Réalisation morphologique et interaction des contraintes* - Hasna Kadimi

-   *Vocalization of Verb Stems Across the Arabic Continuum: Toward a Formal Account of Dialectal Variation* - Charles Vancaeyzeele, Nicola Lampitelli

-   *Perceptual Salience of Russian Consonants: Evidence from Audiovisual Incongruence* - Elena Riekhakaynen, Elena Zatevalova

-   *Source-oriented gradient similarity avoidance in Slavic allomorph selection* - Aljosa Milenkovic, Michael Becker

-   *On the distribʕution of Dhofari Mehri [ʕ]* - Janet Constance Elizabeth Watson

-   *Spreading Effects as Analogical Patterns: Evidence from Serbo-Croatian Borrowings* - Szilárd Tóth

-   *Interaction between universal metrical constraints and authorial preferences: evidence from Catalan poetry* - Manel Vera-Aguilar

-   *Phonological and Intonational Phrases in Bedja* - Mohamed-Tahir Hamid Ahmed Hamid, Cédric Patin

-   *Vers une nouvelle typologie des contextes de liaison en français* - Marie-Hélène Côté

-   **Keynote Talk** - Markus Pöchtrager

-   *Floating /A/ and OCP-driven vowel Alternation in Tashlhiyt Berber A-plurals* - Hamza Sellami

-   *Breaking the Silence: Just how Empty is an Empty Vowel?* - Fabian Zuk, Heglyn Pimenta

-   *The point of Yod in Modern Hebrew* - Noam Faust

-   *Phonological sonorant z in Turkish* - Göktuğ Börtlü

-   *Fricative epithesis in Parisian French: Some data and a formal proposal* - Mathilde Hutin

-   *Properties of pre-frication as acoustic cues to velar\~uvular contrast* - Ekaterina Shepel

-   *Propriétés phonétiques de la voix craquée dans le système tonal en chinois de Xianju* - Yishan Jin, Damien Chabanal

-   *Children's production as a window onto the internal structure of French Obstruent-Liquid clusters* - Lucie Quellec, Antoine Cochard

-   *Deriving Moroccan Arabic Diminutives from Structural Locality and Skeletal Principles* - Abdelkader Elkhaoua

-   *An OT account of domain-dependent asymmetries in Basque cluster phonotactics* - Jakub Dunin-Borkowski

-   *Tonal information in F1 trajectories in Mandarin* - Chenyu LI, Jalal Al-Tamimi

```{r}
#source("publish.R")
```

# Intrinsic Vowel Pitch

# Things to read

## Intrinsic vowel Pitch

-   Work Chenyu Li: separation F1-F0 for diphthongs in varieties of Chinese

## Devoicing

-   Work of Adèle Jatteau
